---
title: "datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo=FALSE, include=FALSE}

library(rmarkdown)
library(knitr)

```

<p align="justify">
This section offers a detailed accounting of the data in the MAS database. Below, you will find one entry per category. By clicking on a given entry, you will encounter a table with all of the datasets under that category. For example, click in `land cover`. Doing so will give you an accounting of all datasets related to land cover. The table has a lot of different information, such as the temporal range of the data (i.e. `start` and `end`), the spatial resolution (i.e. `resolution`) and and the format (either `grid`, `vector` or `tabular`). Additionally, there is a short `description` of the data and a `data_id`. This last component is the most critical one. This is the string pattern you will need to access the corresponding data, <a href="">as explained in this page</a>. The `index` column specifies the order of the entries in the database, and you can ignore it.
</p>

&nbsp;

<details>
  <summary style="cursor:pointer;"> <font size="+2">Land cover</font> <i class="far fa-plus-square"></i></summary>

| index | data_id                       | resolution  | format | description                          | start      | end        |
|-------|-------------------------------|-------------|--------|--------------------------------------|------------|------------|
| 6     | CCI_history/agriculture       | 0.002777778 | grid   | max. agriculture extent              | 1992-01-01 | 2018-01-01 |
| 7     | CCI_history/desertic          | 0.002777778 | grid   | max. desert extent                   | 1992-01-01 | 2018-01-01 |
| 8     | CCI_history/water             | 0.002777778 | grid   | max. water extent                    | 1992-01-01 | 2018-01-01 |
| 9     | CCI_history/wetlands          | 0.002777778 | grid   | max. wetland extent                  | 1992-01-01 | 2018-01-01 |
| 10    | CCI_landCover_agg/agriculture | 0.008333333 | grid   | % agriculture cover                  | 1992-01-01 | 2018-01-01 |
| 11    | CCI_landCover_agg/forest      | 0.008333333 | grid   | % forest cover                       | 1992-01-01 | 2018-01-01 |
| 12    | CCI_landCover_agg/grassland   | 0.008333333 | grid   | % grassland cover                    | 1992-01-01 | 2018-01-01 |
| 13    | CCI_landCover_agg/shrubland   | 0.008333333 | grid   | % shrubland cover                    | 1992-01-01 | 2018-01-01 |
| 14    | CCI_landCover/landCover       | 0.002777778 | grid   | land cover classification            | 1992-01-01 | 2018-01-01 |
| 40    | GAIA_10as/urbanCover          | 0.002777778 | grid   | % urban cover                        | 1992-01-01 | 2018-01-01 |
| 41    | GAIA_30as/urbanCover          | 0.008333333 | grid   | % urban cover                        | 1992-01-01 | 2018-01-01 |
| 45    | Global_masks/admin            | 0.002777778 | grid   | land maks based on GADM              | NA         | NA         |
| 46    | Global_masks/antarcticIslands | 0.002777778 | grid   | antartic islands mask                | 2019-01-01 | 2019-01-01 |
| 47    | Global_masks/coral            | 0.002777778 | grid   | cold/tropical coral mask             | NA         | NA         |
| 48    | Global_masks/deltas           | 0.002777778 | grid   | coastal delta mask                   | NA         | NA         |
| 49    | Global_masks/estuaries        | 0.002777778 | grid   | estuary mask                         | 2018-01-01 | 2018-01-01 |
| 50    | Global_masks/mangrove         | 0.002777778 | grid   | mangrove mask                        | 1996-01-01 | 2016-01-01 |
| 51    | Global_masks/plantations      | 0.002777778 | grid   | plantation mask                      | 2019-01-01 | 2019-01-01 |
| 52    | Global_masks/reservoirs       | 0.002777778 | grid   | reservoir maks                       | 2019-01-01 | 2019-01-01 |
| 53    | Global_masks/salineLakes      | 0.002777778 | grid   | saline lake mask                     | 2019-01-01 | 2019-01-01 |
| 231   | SEDAC_pastures/pastures       | 0.002777778 | grid   | % pastureland                        | 2000-01-01 | 2000-01-01 |
| 247   | VCF5KYR/NonTreeVegetation     | 0.05        | grid   | % of non-tree vegetation             | 1982-01-01 | 2016-01-01 |
| 248   | VCF5KYR/NonVegetated          | 0.05        | grid   | % of non-vegetated surfaces          | 1982-01-01 | 2016-01-01 |
| 249   | VCF5KYR/TreeCover             | 0.05        | grid   | % of tree cover                      | 1982-01-01 | 2016-01-01 |
| 250   | waterFeatures/cannal          | 0.002777778 | grid   | % of cannals                         | NA         | NA         |
| 251   | waterFeatures/lake            | 0.002777778 | grid   | % of lakes                           | NA         | NA         |
| 252   | waterFeatures/river           | 0.002777778 | grid   | % of rivers                          | NA         | NA         |
| 253   | waterFeatures/tidal           | 0.002777778 | grid   | % of tidal flats                     | NA         | NA         |
| 254   | waterHistory/maxExtent        | 0.002777778 | grid   | max. historical % of water           | 1986-01-01 | 2018-01-01 |
| 255   | waterHistory/permanentWater   | 0.002777778 | grid   | max. historical % of permanent water | 1986-01-01 | 2018-01-01 |
| 256   | waterHistory/seasonalFreq     | 0.002777778 | grid   | % of years with seasonal water       | 1992-01-01 | 2018-01-01 |
| 257   | mapBiomas/amazonia            | 0.000269495 | grid   | land cover of Amazonia, Brazil       | 1985-01-01 | 2018-01-01 |
| 258   | mapBiomas/caatinga            | 0.000269496 | grid   | land cover of Caatinga, Brazil       | 1985-01-01 | 2018-01-01 |
| 259   | mapBiomas/cerrado             | 0.000269496 | grid   | land cover of Cerrado, Brazil        | 1985-01-01 | 2018-01-01 |
| 260   | mapBiomas/mataatlantica       | 0.000269496 | grid   | land cover of Mataatlantica, Brazil  | 1985-01-01 | 2018-01-01 |
| 261   | mapBiomas/pampa               | 0.000269492 | grid   | land cover of Pampa, Brazil          | 1985-01-01 | 2018-01-01 |
| 262   | mapBiomas/pantanal            | 0.000269491 | grid   | land cover of Pantanal, Brazil       | 1985-01-01 | 2018-01-01 |

</details>



<details>
  <summary style="cursor:pointer;"> <font size="+2">Water</font> <i class="far fa-plus-square"></i></summary>
  
| index | data_id                   | resolution  | format | description           | start      | end        |
|-------|---------------------------|-------------|--------|-----------------------|------------|------------|
| 54    | globalRivers/riverDensity | 0.002777778 | grid   | % of river cover      | NA         | NA         |
| 190   | iGSW_10as/permanent       | 0.002777778 | grid   | % of permanent water  | 1992-01-01 | 2018-01-01 |
| 191   | iGSW_10as/seasonal        | 0.002777778 | grid   | % of seasonal water   | 1992-01-01 | 2018-01-01 |
| 192   | iGSW_30as/permanent       | 0.008333333 | grid   | % fof permanent water | 1992-01-01 | 2018-01-01 |
| 37    | FLO1K/max                 | 0.5         | grid   | max. river discharge  | 1992-01-01 | 2015-01-01 |
| 38    | FLO1K/mean                | 0.5         | grid   | mean river discharge  | 1992-01-01 | 2015-01-01 |
| 39    | FLO1K/min                 | 0.5         | grid   | min. river discharge  | 1992-01-01 | 2015-01-01 |
| 237   | surfaceWater/missingData  | 0.002777778 | grid   | % of missing data     | 1992-01-01 | 2018-01-01 |
| 238   | surfaceWater/permanent    | 0.002777778 | grid   | % of permanent water  | 1992-01-01 | 2018-01-01 |
| 239   | surfaceWater/seasonal     | 0.002777778 | grid   | % of seasonal water   | 1992-01-01 | 2018-01-01 |
| 244   | tidalFlats/tidalFlats     | 0.002777778 | grid   | % of tidal flats      | 1984-01-01 | 2016-01-01 |

</details>



<details>
  <summary style="cursor:pointer;"> <font size="+2">Elevation</font> <i class="far fa-plus-square"></i></summary>
  
| index | data_id                            | resolution  | format | description                              | start      | end        |
|-------|------------------------------------|-------------|--------|------------------------------------------|------------|------------|
| 212   | meElevation_10as/elevationMax      | 0.002777778 | grid   | max. elevation                           | 2018-01-01 | 2018-01-01 |
| 213   | meElevation_10as/elevationMean     | 0.002777778 | grid   | mean. Elevation                          | 2018-01-01 | 2018-01-01 |
| 214   | meElevation_10as/elevationMin      | 0.002777778 | grid   | min. elevation                           | 2018-01-01 | 2018-01-01 |
| 215   | meElevation_10as/slope             | 0.002777778 | grid   | slope                                    | 2018-01-01 | 2018-01-01 |
| 216   | meElevation_10as/smoothSlope       | 0.002777778 | grid   | mean slope with a 3x3 window mean filter | 2018-01-01 | 2018-01-01 |
| 217   | meElevation_30as/elevationMax      | 0.008333333 | grid   | max. elevation                           | 2018-01-01 | 2018-01-01 |
| 218   | meElevation_30as/elevationMean     | 0.008333333 | grid   | mean elevantion                          | 2018-01-01 | 2018-01-01 |
| 219   | meElevation_30as/elevationMeanLand | 0.008333333 | grid   | mean elevantion on land                  | 2018-01-01 | 2018-01-01 |
| 220   | meElevation_30as/elevationMin      | 0.008333333 | grid   | min. elevation                           | 2018-01-01 | 2018-01-01 |
| 221   | meElevation_30as/hillshade         | 0.008333333 | grid   | hillshade                                | 2018-01-01 | 2018-01-01 |
| 222   | meElevation_30as/slopeMean         | 0.008333333 | grid   | mean slope                               | 2018-01-01 | 2018-01-01 |
| 223   | MERIT_rivers/riverDensity          | 0.002777778 | grid   | % of river cover                         | NA         | NA         |
| 224   | mountains/k1Class                  | 0.002777778 | grid   | k1 montain classification                | NA         | NA         |
| 225   | mountains/k2Class                  | 0.002777778 | grid   | k2 montain classification                | NA         | NA         |
| 226   | mountains/k3Class                  | 0.002777778 | grid   | k3 mountain classification               | NA         | NA         |
| 211   | meElevation_10as/coastalFlats      | 0.002777778 | grid   | mask of coastal flats based              | 2017-01-01 | 2017-01-01 |

</details>



<details>
  <summary style="cursor:pointer;"> <font size="+2">Climate</font> <i class="far fa-plus-square"></i></summary>
  
| index | data_id                           | resolution  | format | description                            | start      | end        |
|-------|-----------------------------------|-------------|--------|----------------------------------------|------------|------------|
| 1     | BECK_climateMap/futureClass       | 0.008333333 | grid   | climate map (future)                   | 2071-01-01 | 2100-01-01 |
| 2     | BECK_climateMap/futureConfidence  | 0.008333333 | grid   | climate map uncertainty (future)       | 2071-01-01 | 2100-01-01 |
| 3     | BECK_climateMap/presentClass      | 0.008333333 | grid   | climate map (present)                  | 1986-01-01 | 2016-01-01 |
| 4     | BECK_climateMap/presentConfidence | 0.008333333 | grid   | climate map uncertainty (present)      | 1986-01-01 | 2016-01-01 |
| 5     | BECK_climateMap/smoothPresent     | 0.008333333 | grid   | modified climate map (present)         | 1986-01-01 | 2016-01-01 |
| 15    | CHELSA_pClimate/drySeasonLength   | 0.008333333 | grid   | length of dry season (months)          | 1992-01-01 | 2013-01-01 |
| 16    | CHELSA_pClimate/summerMax         | 0.008333333 | grid   | max. summer precipitation              | 1992-01-01 | 2013-01-01 |
| 17    | CHELSA_pClimate/summerMin         | 0.008333333 | grid   | min. summer precipitation              | 1992-01-01 | 2013-01-01 |
| 18    | CHELSA_pClimate/summerTotal       | 0.008333333 | grid   | total summer precipitation             | 1992-01-01 | 2013-01-01 |
| 19    | CHELSA_pClimate/winterMax         | 0.008333333 | grid   | max. winter precipitation              | 1992-01-01 | 2013-01-01 |
| 20    | CHELSA_pClimate/winterMin         | 0.008333333 | grid   | min. winter precipitation              | 1992-01-01 | 2013-01-01 |
| 21    | CHELSA_pClimate/winterTotal       | 0.008333333 | grid   | total winter precipitation             | 1992-01-01 | 2013-01-01 |
| 22    | CHELSA_pClimate/yearMax           | 0.008333333 | grid   | max. year precipitation                | 1992-01-01 | 2013-01-01 |
| 23    | CHELSA_pClimate/yearMin           | 0.008333333 | grid   | min. year precipitation                | 1992-01-01 | 2013-01-01 |
| 24    | CHELSA_pClimate/yearTotal         | 0.008333333 | grid   | total year precipitation               | 1992-01-01 | 2013-01-01 |
| 25    | CHELSA_prec/precipitation         | 0.008333333 | grid   | monthly precipitation                  | 1992-01-01 | 2013-12-01 |
| 26    | CHELSA_tClimate/nrMonthsAbove10c  | 0.008333333 | grid   | nr. of months > 10C                    | 1992-01-01 | 2013-01-01 |
| 27    | CHELSA_tClimate/summerMax         | 0.008333333 | grid   | max. summer temperature                | 1992-01-01 | 2013-01-01 |
| 28    | CHELSA_tClimate/summerMean        | 0.008333333 | grid   | mean summer temperature                | 1992-01-01 | 2013-01-01 |
| 29    | CHELSA_tClimate/summerMin         | 0.008333333 | grid   | min. summer temperature                | 1992-01-01 | 2013-01-01 |
| 30    | CHELSA_tClimate/winterMax         | 0.008333333 | grid   | max. winter temperature                | 1992-01-01 | 2013-01-01 |
| 31    | CHELSA_tClimate/winterMean        | 0.008333333 | grid   | mean winter temperature                | 1992-01-01 | 2013-01-01 |
| 32    | CHELSA_tClimate/winterMin         | 0.008333333 | grid   | min. winter temperature                | 1992-01-01 | 2013-01-01 |
| 33    | CHELSA_tClimate/yearMax           | 0.008333333 | grid   | max. year temperature                  | 1992-01-01 | 2013-01-01 |
| 34    | CHELSA_tClimate/yearMean          | 0.008333333 | grid   | mean year temperature                  | 1992-01-01 | 2013-01-01 |
| 35    | CHELSA_tClimate/yearMin           | 0.008333333 | grid   | min. year temperature                  | 1992-01-01 | 2013-01-01 |
| 36    | CHELSA_tmean/temperature          | 0.008333333 | grid   | mean monthly temperature               | 1992-01-01 | 2013-12-01 |
| 232   | snowCover/maximum                 | 0.002777778 | grid   | max. % of snow cover                   | 2000-01-01 | 2019-01-01 |
| 233   | snowCover/recurrence              | 0.002777778 | grid   | per-pixel recurrence of snow (% years) | 2000-01-01 | 2019-01-01 |
| 240   | TerraClim_PDSI_2am/maxPDSI        | 0.041666667 | grid   | max. Palmer Drought Severity Index     | 1992-01-01 | 2018-01-01 |
| 241   | TerraClim_PDSI_2am/minPDSI        | 0.041666667 | grid   | min. Palmer Drought Severity Index     | 1992-01-01 | 2018-01-01 |
| 242   | TerraClim_PDSI_30am/maxPDSI       | 0.5000004   | grid   | max. Palmer Drought Severity Index     | 1992-01-01 | 2018-01-01 |
| 243   | TerraClim_PDSI_30am/minPDSI       | 0.5000004   | grid   | min. Palmer Drought Severity Index     | 1992-01-01 | 2018-01-01 |

</details>



<details>
  <summary style="cursor:pointer;"> <font size="+2">Ocean</font> <i class="far fa-plus-square"></i></summary>
  
| index | data_id                  | resolution  | format | description                      | start      | end        |
|-------|--------------------------|-------------|--------|----------------------------------|------------|------------|
| 230   | seafloor/seafloor        | 0.002777778 | grid   | classification of sea morphology | NA         | NA         |
| 245   | tidalRanges/avgAmplitude | 0.002777778 | grid   | average tidal amplitude (m)      | 2017-01-01 | 2017-01-01 |

</details>



<details>
  <summary style="cursor:pointer;"> <font size="+2">Boundaries</font> <i class="far fa-plus-square"></i></summary>
  
| index | data_id          | resolution | format | description                   | start | end |
|-------|------------------|------------|--------|-------------------------------|-------|-----|
| 264   | GADM/continents  | NA         | vector | continent boundaries          | NA    | NA  |
| 265   | GADM/leve0simple | NA         | vector | country boundaries (smoothed) | NA    | NA  |
| 266   | GADM/level0      | NA         | vector | country boundaries            | NA    | NA  |
| 267   | GADM/level1      | NA         | vector | country level 1 admin.        | NA    | NA  |
| 268   | GADM/level2      | NA         | vector | country level 2 admin.        | NA    | NA  |
| 269   | GADM/level3      | NA         | vector | country level 3 admin.        | NA    | NA  |
| 270   | GADM/level4      | NA         | vector | country level 4 admin.        | NA    | NA  |
| 271   | GADM/level5      | NA         | vector | country level 5 admin.        | NA    | NA  |
| 272   | GADM/UNRegions   | NA         | vector | UN region boundaries          | NA    | NA  |

</details>



<details>
  <summary style="cursor:pointer;"> <font size="+2">Soil</font> <i class="far fa-plus-square"></i></summary>
  
| index | data_id               | dataset | subdataset    | resolution  | format | category | description          | start      | end        |
|-------|-----------------------|---------|---------------|-------------|--------|----------|----------------------|------------|------------|
| 234   | soilMap/salineSoils   | soilMap | salineSoils   | 0.002777778 | grid   | soil     | mask of saline souls | NA         | NA         |
| 235   | soilMap/soilDepth     | soilMap | soilDepth     | 0.002777778 | grid   | soil     | soil depth (m)       | 2015-01-01 | 2015-01-01 |
| 236   | soilMap/soilDepthMean | soilMap | soilDepthMean | 0.008333333 | grid   | soil     | mean soil depth (m)  | 2015-01-01 | 2015-01-01 |

</details>



<details>
  <summary style="cursor:pointer;"> <font size="+2">Population</font> <i class="far fa-plus-square"></i></summary>
  
| index | data_id               | resolution  | format | description                                              | start      | end        |
|-------|-----------------------|-------------|--------|----------------------------------------------------------|------------|------------|
| 42    | GHS_BUILT/GHSB        | 0.002777778 | grid   | build-up area historical classification                  | 1975-01-01 | 2015-01-01 |
| 43    | GHS_POP/GHSP          | 0.002777778 | grid   | population density                                       | 1975-01-01 | 2015-01-01 |
| 44    | GHS_SMOD/SMOD         | 0.002777778 | grid   | degree of urbanization classification                    | 1975-01-01 | 2015-01-01 |
| 189   | iGHS_POP/GHSP         | 0.008333333 | grid   | linearly interpolated population density                 | 1992-01-01 | 2018-01-01 |
| 246   | travelTime/travelTime | 0.008333333 | grid   | travel time to nearest city with > 50,000 hab. (minutes) | 2000-01-01 | 2015-01-01 |

</details>



<details>
  <summary style="cursor:pointer;"> <font size="+2">Biota</font> <i class="far fa-plus-square"></i></summary>
  
| index | data_id                           | resolution  | format | description                                                                                        | start      | end        |
|-------|-----------------------------------|-------------|--------|----------------------------------------------------------------------------------------------------|------------|------------|
| 263   | BIEN_rangeMaps/BIEN_rangeMaps     | NA          | vector | BIEN database range maps                                                                           | NA         | NA         |
| 273   | IUCN_habRange/actinopterygii      | NA          | vector | IUCN range maps for actinopterygii                                                                 | NA         | NA         |
| 274   | IUCN_habRange/amphibians          | NA          | vector | IUCN range maps for amphibians                                                                     | NA         | NA         |
| 275   | IUCN_habRange/aves                | NA          | vector | IUCN range maps for aves                                                                           | NA         | NA         |
| 276   | IUCN_habRange/cephalaspidomorphi  | NA          | vector | IUCN range maps for cephalaspidomorphi                                                             | NA         | NA         |
| 277   | IUCN_habRange/charophyaceae       | NA          | vector | IUCN range maps for charophyaceae                                                                  | NA         | NA         |
| 278   | IUCN_habRange/chlorophyceae       | NA          | vector | IUCN range maps for chlorophyceae                                                                  | NA         | NA         |
| 279   | IUCN_habRange/chondrichthyes      | NA          | vector | IUCN range maps for chondrichthyes                                                                 | NA         | NA         |
| 280   | IUCN_habRange/liliopsida          | NA          | vector | IUCN range maps for liliopsida                                                                     | NA         | NA         |
| 281   | IUCN_habRange/lycopodiopsida      | NA          | vector | IUCN range maps for lycopodiopsida                                                                 | NA         | NA         |
| 282   | IUCN_habRange/magnoliopsida       | NA          | vector | IUCN range maps for magnoliopsida                                                                  | NA         | NA         |
| 283   | IUCN_habRange/mammalia            | NA          | vector | IUCN range maps for mammalia                                                                       | NA         | NA         |
| 284   | IUCN_habRange/marchantiopsida     | NA          | vector | IUCN range maps for marchantiopsida                                                                | NA         | NA         |
| 285   | IUCN_habRange/myxini              | NA          | vector | IUCN range maps for myxini                                                                         | NA         | NA         |
| 286   | IUCN_habRange/pinopsida           | NA          | vector | IUCN range maps for pinopsida                                                                      | NA         | NA         |
| 287   | IUCN_habRange/plantae             | NA          | vector | IUCN range maps for plantae                                                                        | NA         | NA         |
| 288   | IUCN_habRange/polypodiopsida      | NA          | vector | IUCN range maps for polypodiopsida                                                                 | NA         | NA         |
| 289   | IUCN_habRange/reptilia            | NA          | vector | IUCN range maps for reptilia                                                                       | NA         | NA         |
| 290   | IUCN_habRange/sarcopterygii       | NA          | vector | IUCN range maps for sarcopterygii                                                                  | NA         | NA         |
| 291   | IUCN_habRange/ulvophyceae         | NA          | vector | IUCN range maps for ulvophyceae                                                                    | NA         | NA         |
| 55    | GlobES_area/0101                  | 0.008333333 | grid   | Forest - Boreal area (ha)                                                                          | 1992-01-01 | 2018-01-01 |
| 56    | GlobES_area/0102                  | 0.008333333 | grid   | Forest - Subarctic area (ha)                                                                       | 1992-01-01 | 2018-01-01 |
| 57    | GlobES_area/0103                  | 0.008333333 | grid   | Forest - Subantarctic area (ha)                                                                    | 1992-01-01 | 2018-01-01 |
| 58    | GlobES_area/0104                  | 0.008333333 | grid   | Forest - Temperate area (ha)                                                                       | 1992-01-01 | 2018-01-01 |
| 59    | GlobES_area/0105                  | 0.008333333 | grid   | Forest - Subtropical/Tropical Dry area (ha)                                                        | 1992-01-01 | 2018-01-01 |
| 60    | GlobES_area/0106                  | 0.008333333 | grid   | Forest - Subtropical/Tropical Moist Lowland area (ha)                                              | 1992-01-01 | 2018-01-01 |
| 61    | GlobES_area/0107                  | 0.008333333 | grid   | Forest - Subtropical/Tropical Mangrove Vegetation Above High Tide Level   area (ha)                | 1992-01-01 | 2018-01-01 |
| 62    | GlobES_area/0108                  | 0.008333333 | grid   | Forest - Subtropical/Tropical Swamp area (ha)                                                      | 1992-01-01 | 2018-01-01 |
| 63    | GlobES_area/0109                  | 0.008333333 | grid   | Forest - Subtropical/Tropical Moist Montane area (ha)                                              | 1992-01-01 | 2018-01-01 |
| 64    | GlobES_area/0201                  | 0.008333333 | grid   | Savanna - Dry area (ha)                                                                            | 1992-01-01 | 2018-01-01 |
| 65    | GlobES_area/0202                  | 0.008333333 | grid   | Savanna - Moist area (ha)                                                                          | 1992-01-01 | 2018-01-01 |
| 66    | GlobES_area/0301                  | 0.008333333 | grid   | Shrubland - Subarctic area (ha)                                                                    | 1992-01-01 | 2018-01-01 |
| 67    | GlobES_area/0302                  | 0.008333333 | grid   | Shrubland - Subantarctic area (ha)                                                                 | 1992-01-01 | 2018-01-01 |
| 68    | GlobES_area/0303                  | 0.008333333 | grid   | Shrubland - Boreal area (ha)                                                                       | 1992-01-01 | 2018-01-01 |
| 69    | GlobES_area/0304                  | 0.008333333 | grid   | Shrubland - Temperate area (ha)                                                                    | 1992-01-01 | 2018-01-01 |
| 70    | GlobES_area/0305                  | 0.008333333 | grid   | Shrubland - Subtropical/Tropical Dry area (ha)                                                     | 1992-01-01 | 2018-01-01 |
| 71    | GlobES_area/0306                  | 0.008333333 | grid   | Shrubland - Subtropical/Tropical Moist area (ha)                                                   | 1992-01-01 | 2018-01-01 |
| 72    | GlobES_area/0307                  | 0.008333333 | grid   | Shrubland - Subtropical/Tropical High Altitude area (ha)                                           | 1992-01-01 | 2018-01-01 |
| 73    | GlobES_area/0308                  | 0.008333333 | grid   | Shrubland - Mediterranean-type Shrubby Vegetation area (ha)                                        | 1992-01-01 | 2018-01-01 |
| 74    | GlobES_area/0401                  | 0.008333333 | grid   | Grassland - Tundra area (ha)                                                                       | 1992-01-01 | 2018-01-01 |
| 75    | GlobES_area/0402                  | 0.008333333 | grid   | Grassland - Subarctic area (ha)                                                                    | 1992-01-01 | 2018-01-01 |
| 76    | GlobES_area/0403                  | 0.008333333 | grid   | Grassland - Subantarctic area (ha)                                                                 | 1992-01-01 | 2018-01-01 |
| 77    | GlobES_area/0404                  | 0.008333333 | grid   | Grassland - Temperate area (ha)                                                                    | 1992-01-01 | 2018-01-01 |
| 78    | GlobES_area/0405                  | 0.008333333 | grid   | Grassland - Subtropical/Tropical Dry area (ha)                                                     | 1992-01-01 | 2018-01-01 |
| 79    | GlobES_area/0406                  | 0.008333333 | grid   | Grassland - Subtropical/Tropical Seasonally Wet/Flooded area (ha)                                  | 1992-01-01 | 2018-01-01 |
| 80    | GlobES_area/0407                  | 0.008333333 | grid   | Grassland - Subtropical/Tropical High Altitude area (ha)                                           | 1992-01-01 | 2018-01-01 |
| 81    | GlobES_area/0501                  | 0.008333333 | grid   | Wetlands (inland) - Permanent Rivers/Streams/Creeks (includes waterfalls)   area (ha)              | 1992-01-01 | 2018-01-01 |
| 82    | GlobES_area/0502                  | 0.008333333 | grid   | Wetlands (inland) - Seasonal/Intermittent/Irregular Rivers/Streams/Creeks   area (ha)              | 1992-01-01 | 2018-01-01 |
| 83    | GlobES_area/0504                  | 0.008333333 | grid   | Wetlands (inland) - Bogs, Marshes, Swamps, Fens, Peatlands area (ha)                               | 1992-01-01 | 2018-01-01 |
| 84    | GlobES_area/0505                  | 0.008333333 | grid   | Wetlands (inland) - Permanent Freshwater Lakes (over 8ha) area (ha)                                | 1992-01-01 | 2018-01-01 |
| 85    | GlobES_area/0506                  | 0.008333333 | grid   | Wetlands (inland) - Seasonal/Intermittent Freshwater Lakes (over 8ha)   area (ha)                  | 1992-01-01 | 2018-01-01 |
| 86    | GlobES_area/0507                  | 0.008333333 | grid   | Wetlands (inland) - Permanent Freshwater Marshes/Pools (under 8ha) area   (ha)                     | 1992-01-01 | 2018-01-01 |
| 87    | GlobES_area/0508                  | 0.008333333 | grid   | Wetlands (inland) - Seasonal/Intermittent Freshwater Marshes/Pools (under   8ha) area (ha)         | 1992-01-01 | 2018-01-01 |
| 88    | GlobES_area/0510                  | 0.008333333 | grid   | Wetlands (inland) - Tundra Wetlands (incl. pools and temporary waters   from snowmelt) area (ha)   | 1992-01-01 | 2018-01-01 |
| 89    | GlobES_area/0511                  | 0.008333333 | grid   | Wetlands (inland) - Alpine Wetlands (includes temporary waters from   snowmelt) area (ha)          | 1992-01-01 | 2018-01-01 |
| 90    | GlobES_area/0514                  | 0.008333333 | grid   | Wetlands (inland) - Permanent Saline, Brackish or Alkaline Lakes area   (ha)                       | 1992-01-01 | 2018-01-01 |
| 91    | GlobES_area/0515                  | 0.008333333 | grid   | Wetlands (inland) - Seasonal/Intermittent Saline, Brackish or Alkaline   Lakes and Flats area (ha) | 1992-01-01 | 2018-01-01 |
| 92    | GlobES_area/0516                  | 0.008333333 | grid   | Wetlands (inland) - Permanent Saline, Brackish or Alkaline Marshes/Pools   area (ha)               | 1992-01-01 | 2018-01-01 |
| 93    | GlobES_area/0517                  | 0.008333333 | grid   | Wetlands (inland) - Seasonal/Intermittent Saline, Brackish or Alkaline   Marshes/Pools area (ha)   | 1992-01-01 | 2018-01-01 |
| 94    | GlobES_area/0600                  | 0.008333333 | grid   | Rocky areas (eg. inland cliffs, mountain peaks) area (ha)                                          | 1992-01-01 | 2018-01-01 |
| 95    | GlobES_area/0801                  | 0.008333333 | grid   | Desert - Hot area (ha)                                                                             | 1992-01-01 | 2018-01-01 |
| 96    | GlobES_area/0802                  | 0.008333333 | grid   | Desert - Temperate area (ha)                                                                       | 1992-01-01 | 2018-01-01 |
| 97    | GlobES_area/0803                  | 0.008333333 | grid   | Desert - Cold area (ha)                                                                            | 1992-01-01 | 2018-01-01 |
| 98    | GlobES_area/0908                  | 0.008333333 | grid   | Marine Neritic - Coral Reef area (ha)                                                              | 1992-01-01 | 2018-01-01 |
| 99    | GlobES_area/0910                  | 0.008333333 | grid   | Marine Neritic - Estuaries area (ha)                                                               | 1992-01-01 | 2018-01-01 |
| 100   | GlobES_area/1001                  | 0.008333333 | grid   | Marine Oceanic - Epipelagic (0–200 m) area (ha)                                                    | 1992-01-01 | 2018-01-01 |
| 101   | GlobES_area/1002                  | 0.008333333 | grid   | Marine Oceanic - Mesopelagic (200–1,000 m) area (ha)                                               | 1992-01-01 | 2018-01-01 |
| 102   | GlobES_area/1003                  | 0.008333333 | grid   | Marine Oceanic - Bathypelagic (1,000–4,000 m) area (ha)                                            | 1992-01-01 | 2018-01-01 |
| 103   | GlobES_area/1004                  | 0.008333333 | grid   | Marine Oceanic - Abyssopelagic (4,000–6,000 m) area (ha)                                           | 1992-01-01 | 2018-01-01 |
| 104   | GlobES_area/1101                  | 0.008333333 | grid   | Marine Deep Benthic - Continental Slope/Bathyl Zone (200-4,000m) area   (ha)                       | 1992-01-01 | 2018-01-01 |
| 105   | GlobES_area/1102                  | 0.008333333 | grid   | Marine Deep Benthic - Abyssal Plain (4,000-6,000m) area (ha)                                       | 1992-01-01 | 2018-01-01 |
| 106   | GlobES_area/1103                  | 0.008333333 | grid   | Marine Deep Benthic - Abyssal Mountain/Hills (4,000-6,000m) area (ha)                              | 1992-01-01 | 2018-01-01 |
| 107   | GlobES_area/1104                  | 0.008333333 | grid   | Marine Deep Benthic - Hadal/Deep Sea Trench (>6,000m) area (ha)                                    | 1992-01-01 | 2018-01-01 |
| 108   | GlobES_area/1105                  | 0.008333333 | grid   | Marine Deep Benthic - Seamount area (ha)                                                           | 1992-01-01 | 2018-01-01 |
| 109   | GlobES_area/1204                  | 0.008333333 | grid   | Marine Intertidal - Mud Flats and Salt Flats area (ha)                                             | 1992-01-01 | 2018-01-01 |
| 110   | GlobES_area/1205                  | 0.008333333 | grid   | Marine Intertidal - Salt Marshes (Emergent Grasses) area (ha)                                      | 1992-01-01 | 2018-01-01 |
| 111   | GlobES_area/1206                  | 0.008333333 | grid   | Marine Intertidal - Tidepools area (ha)                                                            | 1992-01-01 | 2018-01-01 |
| 112   | GlobES_area/1207                  | 0.008333333 | grid   | Marine Intertidal - Mangrove Submerged Roots area (ha)                                             | 1992-01-01 | 2018-01-01 |
| 113   | GlobES_area/1304                  | 0.008333333 | grid   | Marine Coastal/Supratidal - Coastal Brackish/Saline Lagoons/Marine Lakes   area (ha)               | 1992-01-01 | 2018-01-01 |
| 114   | GlobES_area/1305                  | 0.008333333 | grid   | Marine Coastal/Supratidal - Coastal Freshwater Lakes area (ha)                                     | 1992-01-01 | 2018-01-01 |
| 115   | GlobES_area/1401                  | 0.008333333 | grid   | Artificial/Terrestrial - Arable Land area (ha)                                                     | 1992-01-01 | 2018-01-01 |
| 116   | GlobES_area/1402                  | 0.008333333 | grid   | Artificial/Terrestrial - Pastureland area (ha)                                                     | 1992-01-01 | 2018-01-01 |
| 117   | GlobES_area/1405                  | 0.008333333 | grid   | Artificial/Terrestrial - Urban Areas area (ha)                                                     | 1992-01-01 | 2018-01-01 |
| 118   | GlobES_area/1508                  | 0.008333333 | grid   | Artificial/Aquatic - Irrigated Land (includes irrigation channels) area   (ha)                     | 1992-01-01 | 2018-01-01 |
| 119   | GlobES_area/1511                  | 0.008333333 | grid   | Artificial/Marine - Marine Anthropogenic Structures area (ha)                                      | 1992-01-01 | 2018-01-01 |
| 120   | GlobES_dominantEco/dominantEco    | 0.008333333 | grid   | per-pixel domiant ecosystem                                                                        | 1992-01-01 | 2018-01-01 |
| 121   | GlobES_ecoTransitions/changeCount | 0.008333333 | grid   | nr. Of changes n=in ecosystem dominance                                                            | 1992-01-01 | 2018-01-01 |
| 122   | GlobES_ecoTransitions/changeType  | 0.008333333 | grid   | type of change in ecosystem dominance                                                              | 1992-01-01 | 2018-01-01 |
| 123   | GlobES_ecoTransitions/transitions | 0.008333333 | grid   | changes in ecosystem dominance                                                                     | 1992-01-01 | 2018-01-01 |
| 124   | GlobES_qa/0101                    | 0.008333333 | grid   | Forest - Boreal change QA                                                                          | 1993-01-01 | 2018-01-01 |
| 125   | GlobES_qa/0102                    | 0.008333333 | grid   | Forest - Subarctic change QA                                                                       | 1993-01-01 | 2018-01-01 |
| 126   | GlobES_qa/0103                    | 0.008333333 | grid   | Forest - Subantarctic change QA                                                                    | 1993-01-01 | 2018-01-01 |
| 127   | GlobES_qa/0104                    | 0.008333333 | grid   | Forest - Temperate change QA                                                                       | 1993-01-01 | 2018-01-01 |
| 128   | GlobES_qa/0105                    | 0.008333333 | grid   | Forest - Subtropical/Tropical Dry change QA                                                        | 1993-01-01 | 2018-01-01 |
| 129   | GlobES_qa/0106                    | 0.008333333 | grid   | Forest - Subtropical/Tropical Moist Lowland change QA                                              | 1993-01-01 | 2018-01-01 |
| 130   | GlobES_qa/0107                    | 0.008333333 | grid   | Forest - Subtropical/Tropical Mangrove Vegetation Above High Tide Level   change QA                | 1993-01-01 | 2018-01-01 |
| 131   | GlobES_qa/0108                    | 0.008333333 | grid   | Forest - Subtropical/Tropical Swamp change QA                                                      | 1993-01-01 | 2018-01-01 |
| 132   | GlobES_qa/0109                    | 0.008333333 | grid   | Forest - Subtropical/Tropical Moist Montane change QA                                              | 1993-01-01 | 2018-01-01 |
| 133   | GlobES_qa/0201                    | 0.008333333 | grid   | Savanna - Dry change QA                                                                            | 1993-01-01 | 2018-01-01 |
| 134   | GlobES_qa/0202                    | 0.008333333 | grid   | Savanna - Moist change QA                                                                          | 1993-01-01 | 2018-01-01 |
| 135   | GlobES_qa/0301                    | 0.008333333 | grid   | Shrubland - Subarctic change QA                                                                    | 1993-01-01 | 2018-01-01 |
| 136   | GlobES_qa/0302                    | 0.008333333 | grid   | Shrubland - Subantarctic change QA                                                                 | 1993-01-01 | 2018-01-01 |
| 137   | GlobES_qa/0303                    | 0.008333333 | grid   | Shrubland - Boreal change QA                                                                       | 1993-01-01 | 2018-01-01 |
| 138   | GlobES_qa/0304                    | 0.008333333 | grid   | Shrubland - Temperate change QA                                                                    | 1993-01-01 | 2018-01-01 |
| 139   | GlobES_qa/0305                    | 0.008333333 | grid   | Shrubland - Subtropical/Tropical Dry change QA                                                     | 1993-01-01 | 2018-01-01 |
| 140   | GlobES_qa/0306                    | 0.008333333 | grid   | Shrubland - Subtropical/Tropical Moist change QA                                                   | 1993-01-01 | 2018-01-01 |
| 141   | GlobES_qa/0307                    | 0.008333333 | grid   | Shrubland - Subtropical/Tropical High Altitude change QA                                           | 1993-01-01 | 2018-01-01 |
| 142   | GlobES_qa/0308                    | 0.008333333 | grid   | Shrubland - Mediterranean-type Shrubby Vegetation change QA                                        | 1993-01-01 | 2018-01-01 |
| 143   | GlobES_qa/0401                    | 0.008333333 | grid   | Grassland - Tundra change QA                                                                       | 1993-01-01 | 2018-01-01 |
| 144   | GlobES_qa/0402                    | 0.008333333 | grid   | Grassland - Subarctic change QA                                                                    | 1993-01-01 | 2018-01-01 |
| 145   | GlobES_qa/0403                    | 0.008333333 | grid   | Grassland - Subantarctic change QA                                                                 | 1993-01-01 | 2018-01-01 |
| 146   | GlobES_qa/0404                    | 0.008333333 | grid   | Grassland - Temperate change QA                                                                    | 1993-01-01 | 2018-01-01 |
| 147   | GlobES_qa/0405                    | 0.008333333 | grid   | Grassland - Subtropical/Tropical Dry change QA                                                     | 1993-01-01 | 2018-01-01 |
| 148   | GlobES_qa/0406                    | 0.008333333 | grid   | Grassland - Subtropical/Tropical Seasonally Wet/Flooded change QA                                  | 1993-01-01 | 2018-01-01 |
| 149   | GlobES_qa/0407                    | 0.008333333 | grid   | Grassland - Subtropical/Tropical High Altitude change QA                                           | 1993-01-01 | 2018-01-01 |
| 150   | GlobES_qa/0501                    | 0.008333333 | grid   | Wetlands (inland) - Permanent Rivers/Streams/Creeks (includes waterfalls)   change QA              | 1993-01-01 | 2018-01-01 |
| 151   | GlobES_qa/0502                    | 0.008333333 | grid   | Wetlands (inland) - Seasonal/Intermittent/Irregular Rivers/Streams/Creeks   change QA              | 1993-01-01 | 2018-01-01 |
| 152   | GlobES_qa/0504                    | 0.008333333 | grid   | Wetlands (inland) - Bogs, Marshes, Swamps, Fens, Peatlands change QA                               | 1993-01-01 | 2018-01-01 |
| 153   | GlobES_qa/0505                    | 0.008333333 | grid   | Wetlands (inland) - Permanent Freshwater Lakes (over 8ha) change QA                                | 1993-01-01 | 2018-01-01 |
| 154   | GlobES_qa/0506                    | 0.008333333 | grid   | Wetlands (inland) - Seasonal/Intermittent Freshwater Lakes (over 8ha)   change QA                  | 1993-01-01 | 2018-01-01 |
| 155   | GlobES_qa/0507                    | 0.008333333 | grid   | Wetlands (inland) - Permanent Freshwater Marshes/Pools (under 8ha) change   QA                     | 1993-01-01 | 2018-01-01 |
| 156   | GlobES_qa/0508                    | 0.008333333 | grid   | Wetlands (inland) - Seasonal/Intermittent Freshwater Marshes/Pools (under   8ha) change QA         | 1993-01-01 | 2018-01-01 |
| 157   | GlobES_qa/0510                    | 0.008333333 | grid   | Wetlands (inland) - Tundra Wetlands (incl. pools and temporary waters   from snowmelt) change QA   | 1993-01-01 | 2018-01-01 |
| 158   | GlobES_qa/0511                    | 0.008333333 | grid   | Wetlands (inland) - Alpine Wetlands (includes temporary waters from   snowmelt) change QA          | 1993-01-01 | 2018-01-01 |
| 159   | GlobES_qa/0514                    | 0.008333333 | grid   | Wetlands (inland) - Permanent Saline, Brackish or Alkaline Lakes change   QA                       | 1993-01-01 | 2018-01-01 |
| 160   | GlobES_qa/0515                    | 0.008333333 | grid   | Wetlands (inland) - Seasonal/Intermittent Saline, Brackish or Alkaline   Lakes and Flats change QA | 1993-01-01 | 2018-01-01 |
| 161   | GlobES_qa/0516                    | 0.008333333 | grid   | Wetlands (inland) - Permanent Saline, Brackish or Alkaline Marshes/Pools   change QA               | 1993-01-01 | 2018-01-01 |
| 162   | GlobES_qa/0517                    | 0.008333333 | grid   | Wetlands (inland) - Seasonal/Intermittent Saline, Brackish or Alkaline   Marshes/Pools change QA   | 1993-01-01 | 2018-01-01 |
| 163   | GlobES_qa/0600                    | 0.008333333 | grid   | Rocky areas (eg. inland cliffs, mountain peaks) change QA                                          | 1993-01-01 | 2018-01-01 |
| 164   | GlobES_qa/0801                    | 0.008333333 | grid   | Desert - Hot change QA                                                                             | 1993-01-01 | 2018-01-01 |
| 165   | GlobES_qa/0802                    | 0.008333333 | grid   | Desert - Temperate change QA                                                                       | 1993-01-01 | 2018-01-01 |
| 166   | GlobES_qa/0803                    | 0.008333333 | grid   | Desert - Cold change QA                                                                            | 1993-01-01 | 2018-01-01 |
| 167   | GlobES_qa/0908                    | 0.008333333 | grid   | Marine Neritic - Coral Reef change QA                                                              | 1993-01-01 | 2018-01-01 |
| 168   | GlobES_qa/0910                    | 0.008333333 | grid   | Marine Neritic - Estuaries change QA                                                               | 1993-01-01 | 2018-01-01 |
| 169   | GlobES_qa/1001                    | 0.008333333 | grid   | Marine Oceanic - Epipelagic (0–200 m) change QA                                                    | 1993-01-01 | 2018-01-01 |
| 170   | GlobES_qa/1002                    | 0.008333333 | grid   | Marine Oceanic - Mesopelagic (200–1,000 m) change QA                                               | 1993-01-01 | 2018-01-01 |
| 171   | GlobES_qa/1003                    | 0.008333333 | grid   | Marine Oceanic - Bathypelagic (1,000–4,000 m) change QA                                            | 1993-01-01 | 2018-01-01 |
| 172   | GlobES_qa/1004                    | 0.008333333 | grid   | Marine Oceanic - Abyssopelagic (4,000–6,000 m) change QA                                           | 1993-01-01 | 2018-01-01 |
| 173   | GlobES_qa/1101                    | 0.008333333 | grid   | Marine Deep Benthic - Continental Slope/Bathyl Zone (200-4,000m) change   QA                       | 1993-01-01 | 2018-01-01 |
| 174   | GlobES_qa/1102                    | 0.008333333 | grid   | Marine Deep Benthic - Abyssal Plain (4,000-6,000m) change QA                                       | 1993-01-01 | 2018-01-01 |
| 175   | GlobES_qa/1103                    | 0.008333333 | grid   | Marine Deep Benthic - Abyssal Mountain/Hills (4,000-6,000m) change QA                              | 1993-01-01 | 2018-01-01 |
| 176   | GlobES_qa/1104                    | 0.008333333 | grid   | Marine Deep Benthic - Hadal/Deep Sea Trench (>6,000m) change QA                                    | 1993-01-01 | 2018-01-01 |
| 177   | GlobES_qa/1105                    | 0.008333333 | grid   | Marine Deep Benthic - Seamount change QA                                                           | 1993-01-01 | 2018-01-01 |
| 178   | GlobES_qa/1204                    | 0.008333333 | grid   | Marine Intertidal - Mud Flats and Salt Flats change QA                                             | 1993-01-01 | 2018-01-01 |
| 179   | GlobES_qa/1205                    | 0.008333333 | grid   | Marine Intertidal - Salt Marshes (Emergent Grasses) change QA                                      | 1993-01-01 | 2018-01-01 |
| 180   | GlobES_qa/1206                    | 0.008333333 | grid   | Marine Intertidal - Tidepools change QA                                                            | 1993-01-01 | 2018-01-01 |
| 181   | GlobES_qa/1207                    | 0.008333333 | grid   | Marine Intertidal - Mangrove Submerged Roots change QA                                             | 1993-01-01 | 2018-01-01 |
| 182   | GlobES_qa/1304                    | 0.008333333 | grid   | Marine Coastal/Supratidal - Coastal Brackish/Saline Lagoons/Marine Lakes   change QA               | 1993-01-01 | 2018-01-01 |
| 183   | GlobES_qa/1305                    | 0.008333333 | grid   | Marine Coastal/Supratidal - Coastal Freshwater Lakes change QA                                     | 1993-01-01 | 2018-01-01 |
| 184   | GlobES_qa/1401                    | 0.008333333 | grid   | Artificial/Terrestrial - Arable Land change QA                                                     | 1993-01-01 | 2018-01-01 |
| 185   | GlobES_qa/1402                    | 0.008333333 | grid   | Artificial/Terrestrial - Pastureland change QA                                                     | 1993-01-01 | 2018-01-01 |
| 186   | GlobES_qa/1405                    | 0.008333333 | grid   | Artificial/Terrestrial - Urban Areas change QA                                                     | 1993-01-01 | 2018-01-01 |
| 187   | GlobES_qa/1508                    | 0.008333333 | grid   | Artificial/Aquatic - Irrigated Land (includes irrigation channels) change   QA                     | 1993-01-01 | 2018-01-01 |
| 188   | GlobES_qa/1511                    | 0.008333333 | grid   | Artificial/Marine - Marine Anthropogenic Structures change QA                                      | 1993-01-01 | 2018-01-01 |

</details>



<details>
  <summary style="cursor:pointer;"> <font size="+2">Other</font> <i class="far fa-plus-square"></i></summary>
  
| index | data_id                          | resolution  | format | description                                                   | start      | end        |
|-------|----------------------------------|-------------|--------|---------------------------------------------------------------|------------|------------|
| 195   | linearDistance_10as/lake         | 0.002777778 | grid   | linear distance to lakes                                      | NA         | NA         |
| 196   | linearDistance_10as/ocean        | 0.002777778 | grid   | linear distance to oceans                                     | NA         | NA         |
| 201   | linearDistance_30as/lake         | 0.008333333 | grid   | linear distance to lakes                                      | NA         | NA         |
| 202   | linearDistance_30as/ocean        | 0.008333333 | grid   | linear distance to oceans                                     | NA         | NA         |
| 193   | linearDistance_10as/coastalFlats | 0.002777778 | grid   | linear distance to coastalFlats                               | NA         | NA         |
| 194   | linearDistance_10as/coral        | 0.002777778 | grid   | linear distance to corals                                     | NA         | NA         |
| 197   | linearDistance_10as/reservoirs   | 0.002777778 | grid   | linear distance to reservoirs                                 | NA         | NA         |
| 198   | linearDistance_10as/river        | 0.002777778 | grid   | linear distance to rivers                                     | NA         | NA         |
| 199   | linearDistance_30as/coastalFlats | 0.008333333 | grid   | linear distance to coastalFlats                               | NA         | NA         |
| 200   | linearDistance_30as/coral        | 0.008333333 | grid   | linear distance to corals                                     | NA         | NA         |
| 203   | linearDistance_30as/reservoirs   | 0.008333333 | grid   | linear distance to reservoirs                                 | NA         | NA         |
| 204   | linearDistance_30as/river        | 0.008333333 | grid   | linear distance to rivers                                     | NA         | NA         |
| 227   | pixelArea_10as/pixelArea         | 0.002777778 | grid   | pixel area (ha)                                               | NA         | NA         |
| 228   | pixelArea_30as/pixelArea         | 0.008333333 | grid   | pixel area (ha)                                               | NA         | NA         |
| 229   | potentialWater/potentialWater    | 0.002777778 | grid   | mask of terrestrial areas including coastal and inland waters | 1992-01-01 | 2018-01-01 |

</details>
