---
title: "data access"
output: rmarkdown::html_vignette
toc: true
vignette: >
  %\VignetteIndexEntry{data access}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include = FALSE, echo=FALSE}

require(masDMT)
require(knitr)
require(kableExtra)

options(dmt.data=paste0(system.file(package = 'masDMT'), '/extdata/'))

```

### Collecting data paths
<p align="justify">
Many packages focus on the access to raster, vector, and tabular data, providing constant updates and improvements. For this reason, `masDMT` does not offer additional data access tools. Instead, it helps users locate relevant data. `list_data()` uses <a href="https://macroecology-society.github.io/data-catalog/"> unique data identifiers as displayed in the MAS data catalog</a> to find and report metadata on the relevant data files, including their format and location. As shown below, we can construct a data call in different levels of complexity, from a generic dataset request to a combination of dataset, subdataset, and spatial resolution.
</p>

```{r, eval=FALSE}
# find all files for dataset "CCI_landCover"
list_data('CCI_landCover/landCover')

# find all files for subdataset "landCover"
list_data('CCI_landCover/landCover')

# find all files for resolution "300m"
list_data('CCI_landCover/landCover/300m')

```

<p align="justify">
A call to a specific resolution can be useful as some datasets might provide multiple options. Below we use the `MERIT_DEM` as an example, which is commonly used at the MAS at both 300-m and 1-km resolutions, and are pre-computed to minized data processing requirements.
<p>

```{r, eval=FALSE}
list_data('MERIT_DEM')
```

```{r, echo=FALSE}
df = head(list_data('MERIT_DEM'))
kable_styling(knitr::kable(df), full_width=F, bootstrap_options=c("striped", "hover", "condensed"), font_size=8)

```

<p align="justify">
This example shows another important application of `list_data()`. It is a useful tool to consult the complexity of the data available in MAS, helping us better refine our requirements. In fact, if no input is provided to the function, this will return the full registry as a `data.frame`.
<p>
