---
title: "finding data"
output: rmarkdown::html_vignette
toc: true
vignette: >
  %\VignetteIndexEntry{finding data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include=FALSE, echo=FALSE}

require(masDMT)
require(knitr)
require(kableExtra)

knitr::opts_chunk$set(fig.path = "man/figures/", echo = TRUE)
register_path(list(dmt.data=system.file(package='masDMT', 'extdata')))

```

### Collecting data paths
<p align="justify">
Many packages focus on the access to raster, vector, and tabular data, providing constant updates and improvements. For this reason, `masDMT` does not offer additional data access tools. Instead, it helps users locate relevant data. `list_data()` uses <a href="https://macroecology-society.github.io/data-catalog/"> unique data identifiers as displayed in the MAS data catalog</a> to find and report metadata on the relevant data files, including their format and location. As shown below, we can construct a data call in different levels of complexity, from a generic dataset request to a combination of dataset, subdataset, and spatial resolution.
</p>

```{r, eval=FALSE}
# find all files for dataset "CCI_landCover"
list_data('CCI_landCover')

# find all files for subdataset "landCover" of dataset "CCI_landCover"
list_data('CCI_landCover/landCover')

# find all files subdataset "landCover" of dataset "CCI_landCover" with a resolution of "300m"
list_data('CCI_landCover/landCover/300m')
```

<p align="justify">
Calling `list_data()` without specifying a dataset call will return a data.frame listing all registered datasets. It is a useful tool to consult the complexity of the available data, helping us refine our search query.
<p>

```{r, eval=FALSE}
list_data()
```

```{r, echo=FALSE}
df = head(list_data('CCI_landCover'))
kable_styling(knitr::kable(df), full_width=F, bootstrap_options=c("striped", "hover", "condensed"), font_size=8)

```
