---
title: "system variables"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{system variables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE, message=FALSE}
library(masDMT)
```

### Configuring local projects ---
<p align="justify">
Environmental variables are seemingly trivial but often overlooked assets. If an argument in your code is recurrent, defining environmental variables is a time saver. For example, consider you have several scripts accessing the same online database, which requires user credentials. If you need to modify those credentials, it can be bothersome to change every single script. As an alternative, we can use R's `options()` to define a variable that contains those credentials. 
</p>
<p align="justify">
`masDMT` takes advantage of this feature to define the path to the MAS database. When we modify the option `dmt.data` in `masDMT`, we can use the package in another project built around a similar data structure without any further changes.
</p>
<p align="justify">
As seen below, there are two commands that you need to know to handle the system path. First, `getOptions()`, which allows you to find specific variables and consult other existing ones. Second, `option()`, which you can use to define new varibales and update exisitng ones. 
</p>

```{r}

# consult the current data path
getOption('dmt.data')

# redefine `dmt.data` as 'new path'
options(dmt.data='new path')

# print the new data path
getOption('dmt.data')

```

<p align="justify">
`masDMT` provides two additional, useful options that can be changed. First, we can change the option `mas.catalog`, which changes the path to the standardized data catalog of the MAS database. This catalog, < href="https://macroecology-society.github.io/data-catalog/">available through GitHub</a>, containst data descriptions for the datasets used at MAS. However, if we wish to keep the catalog locally, we can modify the the `mas.catalog` option to a local copy so that we can work offline. Following the same premise, we can also modity `mas.toolbox`, which links us to his website.
</p>
