---
title: "system variables"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{system variables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE, message=FALSE}
library(masDMT)
```

### Configuring local projects
<p align="justify">
Environmental variables are seemingly trivial but often overlooked assets. If an argument in your code is recurrent, defining environmental variables is a time saver. For example, consider you have several scripts accessing the same online database, which requires user credentials. If you need to modify those credentials, it can be bothersome to change every single script. As an alternative, we can use R's `options()` to define a variable that contains those credentials. 
</p>
<p align="justify">
`masDMT` takes advantage of this feature through the `register_path()`. This function registers paths to the MAS database as well as to relevant documentation. This information is recorded permanently together with your package installation, which prevents you from repeating this step with every script. Every time the `masDMT` loads, the pre-defined variables will be loaded.
</p>
<p align="justify">
To exemplify the use of this tool, let's first register our database, which is located in `/mas/database/`. To register this path, we can use `register_path` as following:
</p>

```{r}
# consult the current data path
register_path(list(dmt.data='/mas/database/'))
```

<p align="justify">
Note the input to the function is in the form of a list, and the keyword `dmt.data` is used to register the database. This is the go-to variable for functions that query the existing database, such as `list_data()`.
</p>

<p align="justify">
`dmt.data` is not the only variable we can set. First, we can change the option `mas.catalog`, which changes the path to the standardized data catalog of the MAS database. This catalog, <a href="https://macroecology-society.github.io/data-catalog/">available through GitHub</a>, contains data descriptions for the datasets used at MAS. However, if we wish to keep the catalog locally - or register a new catalog- we can modify the the `mas.catalog` option. Following the same premise, we can modify `mas.toolbox`, which links us to the website of this package by default.
</p>

```{r, eval=FALSE}
# change path to new catalog website
register_path(list(dmt.catalog='/new_catalog/'))

# change path to new toolbox website
register_path(list(dmt.toolbox='/new_toolbox/'))
```

<p align="justify">
In the previous examples, we changed one variable at a time for the sake of simplicity. However, you can provide all variables at once. Since the input is provided as a list, `register_path()` can update several variables simultaneously, making use of the list names to find the right variable to modify.
</p>

```{r, eval=FALSE}
register_path(list(dmt.data='/mas/database/', dmt.catalog='/new_catalog/', dmt.toolbox='/new_toolbox/'))
```
